---
title: "System Task"
output: html_notebook
---

```{r setup, include=TRUE, echo=TRUE, message = FALSE}
knitr::opts_chunk$set(message = FALSE)
library(tidyverse)
library(here)
library(C50)
library(caret)
source(here::here("01_tidy", "tidy_system.r"))
source(here::here("02_analysis", "helpers.R"))
```

```{r }
system_features <- system_features %>% 
  filter(deflection != "ignore") %>% 
  mutate(deflection = factor(deflection))
  
split <- split_data(data        = system_features,
                    split_ratio = 0.70,
                    seed        = 123)

```

```{r}
raw_variables_labels <- c("deflection",
                          "absorption_and_emission",
                          "n",
                          "n_item",
                          "max_x",     
                          "max_y",
                          "min_x",
                          "min_y",
                          "mean_x",
                          "mean_y",      
                          "n_head",
                          "n_tail",
                          "n_molecule",
                          "n_path",
                          "n_carbon",    
                          "n_methane",
                          "n_nitrogen",
                          "n_sulfur",
                          "x_range",
                          "y_range",     
                          "c_max",
                          "c_mean")
raw <- as.data.frame(split$data[[1]][,raw_variables_labels])

exact_variables_labels <- c("deflection",
                            "absorption_and_emission",
                            "has_htm",
                            "has_ht",
                            "n_htm",
                            "n_ht",
                            "has_htm_ht_diff_pos",
                            "n_htm_ht_diff_pos",
                            "n_ht_diff_pos",
                            "n_ht_diff_neg")

exact <- as.data.frame(split$data[[1]][,exact_variables_labels])

#my_cols <- c("#00AFBB", "#E7B800", "#FC4E07")
my_cols <- c("#00AFBB", "#FC4E07")

pairs(raw[3:22], pch = 19,  cex = 0.5,
       col = alpha(my_cols[raw$deflection], 0.6),
       lower.panel=NULL)

pairs(exact[3:10], pch = 19,
       col = alpha(my_cols[raw$deflection], 0.6),
       lower.panel=NULL)
```


```{r variable}
raw_variables <- c("n",
                   "n_item",
                   "max_x",     
                   "max_y",
                   "min_x",
                   "min_y",
                   "mean_x",
                   "mean_y",      
                   "n_head",
                   "n_tail",
                   "n_molecule",
                   "n_path",
                   "n_carbon",    
                   "n_methane",
                   "n_nitrogen",
                   "n_sulfur",
                   "x_range",
                   "y_range",     
                   "c_max",
                   "c_mean")

exact_variables <- c("has_htm",
                   "has_ht",
                   "n_htm",
                   "n_ht",
                   "has_htm_ht_diff_pos",
                   "n_htm_ht_diff_pos",
                   "n_ht_diff_pos",
                   "n_ht_diff_neg")

```

```{r deflection-raw}
dt_system_raw <- C5.0(x = as.data.frame(split$data[[1]][,raw_variables]), 
                    y = split$data[[1]]$deflection, 
                    trials = 5)

#summary(dt_system_raw)
#plot(dt_system)
```

```{r deflection-exact}
exact_deflection <- as.data.frame(split$data[[2]][,exact_variables])

exact_deflection_summary <-
  exact_deflection %>%
  mutate(score = case_when(has_htm_ht_diff_pos == 1 & 
                             n_ht_diff_neg >= 1~ "accept" ,
                           TRUE ~ "reject"),
         score = factor(score))

#confusionMatrix(data = exact_deflection_summary$score, reference = split$data[[2]]$deflection)




```

Positive predictive value is the number of true positive cases (labeled accept and predicted accept) divided by the sum of all positive calls (sum of accept predictions). If there are many true negatives predicted as accepts, then we are telling teachers that their students "get it" when they don't. We want to maximize overall accuracy, PPV, and specificity (i.e., minimize false positives). 

```{r}
predictions_raw <- predict(dt_system_raw, newdata = as.data.frame(split$data[[2]][,raw_variables]), type = "class")
caret::confusionMatrix(predictions_raw, reference = split$data[[2]]$deflection)

confusionMatrix(data = exact_deflection_summary$score, reference = split$data[[2]]$deflection)
```



